Mariculture farms in the United States

### 2021-12-16 marine/united_states/US_mapping.Rmd
added more info to doc

**There is general info on lease holders, what they farm, and what municipality or city they are in for 6 states:**

 - California: general areas with acreage for commercial farms
 - Oregon: map of places were commercial harvest/growing is allowed
 - Maryland: Have INDIVIDUAL pdf maps of all lease applications and if they were accepted or not...
 - New Jersey: Have pdf maps of all existing shellfish leases and those issued in 2020
 - Massachusetts: Have number of growers per municipality with acreage and species type; also a subset of farms are available in the NE data viewer.
 - South Carolina: Apparently have 9 oyster farms as of 2021

@@

**Couldn't really find any information on 5 states:**

 - Hawaii, Washington, Texas, Louisiana, Mississippi

@@

@@

Offshore aquaculture in Florida

 - As far as I can tell, none yet: https://www.flseagrant.org/aquaculture/openocean/

@@

What we used for global: 
Our Sound, Our Salmon, 2017. [Accessed January 31, 2020] http://www.moldychum.com/violations-prompt-washington-state-cancel-atlantic-salmon-farm-lease/

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/puget_sound.png)

@@

 - These totals really don't match what NOAA reports in their 2019 report... They report 44094 metric tonnes of marine aquaculture production for 2018... versus 203687 from FAO. I think this has to do with NOAA reporting meat weight and FAO reporting live weight (includes shells)
 - https://media.fisheries.noaa.gov/2021-05/FUS2019-FINAL-webready-2.3.pdf?null=
 - NOAA also reports that the Gulf region produces the most marine aquaculture by volume.. which seems problematic for us considering we have very poor data for the Gulf states.
```{r, message=FALSE}
fao_data_all <- read_csv("../../data/fao_aquaculture_clean.csv")

@@

>>>>

**There is general info on lease holders, what they farm, and what municipality or city they are in for 7 states:**

 - California: general areas with acreage for commercial farms
 - Oregon: map of places were commercial harvest/growing is allowed
 - Maryland: Have INDIVIDUAL pdf maps of all lease applications and if they were accepted or not...
 - New Jersey: Have pdf maps of all existing shellfish leases and those issued in 2020
 - Massachusetts: Have number of growers per municipality with acreage and species type; also a subset of farms are available in the NE data viewer.
 - South Carolina: Apparently have 9 oyster farms as of 2021
 - Washington: Approximate locations of commercial net pens.

@@

**Couldn't really find any information on 4 states:**

 - Hawaii, Texas, Louisiana, Mississippi

@@

Locations of commercial marine net pens
 - https://ecology.wa.gov/Water-Shorelines/Shoreline-coastal-management/Aquaculture/Net-pens

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/washington_pens.png)

@@

@@

@@

```{r, message=FALSE}
fao_data_all <- read_csv("../../data/fao_aquaculture_clean.csv")

@@

FAO reports 16 different marine species of production in 2018. Additionally, there were 4 species that were previously harvested but had no harvest for 2018. FAO reports a total of 203687 live weight tonnes for 2018.

NOAA Fisheries of the United States 2019 Report: 
https://media.fisheries.noaa.gov/2021-05/FUS2019-FINAL-webready-2.3.pdf?null=

 - NOAA report 44094 metric tonnes of marine aquaculture production for 2018... versus 203687 from FAO. I think this has to do with NOAA reporting meat weight and FAO reporting live weight (includes shells)
 - NOAA also reports that the Gulf region produces th e most marine aquaculture by volume.. which seems problematic for us considering we have very poor farm level data for the Gulf states.

![gulf](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/us_mariculture.png)

2018 Census of Aquaculture: https://www.nass.usda.gov/Publications/AgCensus/2017/Online_Resources/Aquaculture/Aqua.pdf

 - Table 1 shows aquaculture farms per state, but it is not split between marine and freshwater from what I can tell. Also split by species group (mollusk, crustaceans, etc.)
 - Table 10 shows saltwater acres and number of farms used for aquaculture production. However, there are landlocked states, so we don't know if it is actually marine or on-land saltwater aquaculture. It does seem reasonable that this would be pretty close to the actual number of farms.. 
 - Table 11 shows sources of water, with "Saltwater" included. This is just where the water comes from. 
 - Table 12 mollusks off bottom seems reasonable to think most of these will be in marine environments. Almost all of the states listed are coastal states.

 - It seems like "Mollusks off bottom", "Mollusks on bottom", "Sea vegetables" are the only ones that I am 80% sure are marine farms... 
 - They also have data at the county level. I know this wouldn't be perfect, but we could filter for coastal counties.
